Development of User-Friendly\\System Identification Techniques

### 2016-08-16 front-and-back-matter/acknowledgements.inc.tex
Add epigraphs
Lots of work on CH03
Uniform commands: part 1
Improved MC figures
First part of acks

\chapter{Acknowledgements}
%TODO m2t team
%TODO ELEC
%TODO proffen, technici, secretaressen
%TODO anna/maarten
%TODO office mates
%TODO EIT people
%TODO jury
%TODO christian larsson, istvan, MST
%TODO mikaya
%TODO CST
%TODO Rick, Annemiek, Matthijs, Frank
%TODO Johan
%TODO Tom
%TODO family
%TODO family-in-law
%TODO alexandra
%TODO pixie

>>>>

\chapter{Acknowledgments}
\myEpigraph{We're all going to die, all of us, what a circus! That alone should make us love each other but it doesn't. \\
We are terrorized and flattened by trivialities, we are eaten up by nothing.}{Charles Bukowski}{The Captain is Out to Lunch and \\ the Sailors have taken over the Ship}
% \myEpigraph{In the End, we will remember not the words of our enemies, but the silence of our friends.}{Martin Luther King Jr.}{}

While the preparation of a PhD is for a large part an endeavor of a single person, it is by no means a solitary experience.
Research without collaboration is unthinkable and is unlikely to yield new scientific and technical insights since personal interactions allow new ideas and applications to germinate.

In the first place, I would like to thank my colleagues at the ELEC department for being an outgoing group that has been combining a fond interest for engineering and leisure.
In particular, I am grateful for the great atmosphere in my office and for my office mates over the last few years: Adam, Anna, David, Diane, Ebrahim, Erlyiang, Francesco, Gustavo, Hannes, Maarten, Mark, Matthias, and Maulik (though not all at the same time).
%FIXME anna/maarten SA
%FIXME: adam -> nobody expects the cauchy distribution

%FIXME EIT people: Matthias, Evi, Dave, Hans
%FIXME NnF people

%FIXME proffen, technici, secretaressen

%FIXME mikaya, John
%FIXME christian larsson, istvan

%FIXME Johan
%FIXME Tom

%FIXME Matthijs
%FIXME CST
%FIXME Rick, Annemiek, Frank, Rolf, MST

%FIXME jury

%FIXME m2t team

%FIXME family
%FIXME family-in-law
%FIXME alexandra

And last but not least, I would like to thank our cat Pixie for being an enjoyably crazy critter and for his enthusiasm when bringing home little presents and leaving them either on the floor or even on my pillow while I'm fast asleep.
His intent has been duly noted and appreciated (the nightly hours and contents of those presents, however, were not always equally well-received).
